Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-10-09 paper/paper.tex
few edits

\begin{figure}[t]
  \centering
  \includegraphics[width=0.85\textwidth]{figs/diff-testing-runtimes-2.pdf}
  \caption{\label{fig:workflow}The workflow of the referred differential
testing approach.}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.85\textwidth]{figs/diff-testing-runtimes-2.pdf}
  \caption{\label{fig:workflow}The workflow of the referred differential
testing approach. In this Activity Diagram, the first black clircle is the start of the process, while the last one if the termination of the process. The green boxes mean activites to be done during the differential testing approach. The small black box mean that there are parallel activities (which in the end are combined).}
\end{figure}
